### 2021-07-03 rad-icfp-2021/correctness.tex
writing bit more in correctness section

@@

\begin{definition}{lax functor between concat}
    TODO
\end{definition}

\begin{example}{D as a lax functor}
    TODO
\end{example}

\begin{proposition}{semantic of D syntactic matches D lax functor}
    TODO
\end{proposition}

@@

@@

@@

@@

>>>>

In a similar vein, we form a concategory from the syntactic multicategory for Target.
We then use the universal property of $\ConcatT$ to construct a functor from $\ConcatT$ to this concategory.
This allows us to compare terms of Target UNF and terms of Target. 
$UNF^-1$ arises in this way.

@@

What remains to explain now is the reverse mode transformation between Source UNF and Target UNF.
We construct a functor $D:\ConcatS\to\ConcatT$. 
This functor will easily be shown to compute reverse mode derivatives.
Because terms of Source UNF in $\ConcatS$, we observe the effect of $D$ on them
and show that it matches the syntactic $\Dsynrevsymbol_{\rho}$ 
from Section~\ref{sub:Simple reverse mode transformation}.

\begin{definition}{D as a lax functor}
    TODO
\end{definition}

\begin{proposition}{semantic of syntactic D matches D lax functor}
    TODO
\end{proposition}

@@

First, we start from the correctness of $D$ which is easy to establish, 
and then somehow propagate this information to Source and Target.

\begin{proposition}{Correctness $D$}
    TODO
\end{proposition}

Recall that the intuition from Source UNF is that it consist of terms of Source that also return their context.
From there, the intuition for the Jacobian of a primitive in Target UNF is that it should be the Jacobian of
the corresponding term in Target.

\MH{I don't want to talk too much about the cotangent bundle functor, but to phrase correctness properties clearly I might have to.}

@@

From this, we can now deduce that the composite transformation doing UNF then $D$ and then $UNF^-1$ is correct
in the sense that it produces a term which computes the gradient of the original term.

@@

By inspection of what that composition actually give on terms from Source, 
we show that the previous composition of transformation indeed gives the transformation 
$\directD{\rho}{\Gamma}{Y}$ from Section~\ref{sub:Macro for pure reverse mode transformation}.

@@

Without any more work, the previous claims have shown that 
$\directD{\rho}{\Gamma}{Y}$ is correct.
